---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dsMatchingClient

[![CRAN status](https://www.r-pkg.org/badges/version/dsMatchingClient)](https://CRAN.R-project.org/package=dsMatchingClient)
[![R-CMD-check](https://github.com/roygusinow/dsMatchingClient/actions/workflows/R-CMD-check.yml/badge.svg)](https://github.com/roygusinow/dsMatchingClient/actions/workflows/R-CMD-check.yml)
[![codecov](https://codecov.io/gh/roygusinow/dsMatchingClient/graph/badge.svg?token=19CXOIZ0I9)](https://codecov.io/gh/roygusinow/dsMatchingClient)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

---

## Overview

`dsMatchingClient` provides tools for estimating causal effects using federated generalized linear models (GLMs) and matching methods within the [DataSHIELD](https://www.datashield.org/) infrastructure. The serverside package `dsMatching` implements the necessary server-side functionality, [github.com/roygusinow/dsMatching](https://github.com/roygusinow/dsMatching)

It supports:

* Estimation of ATE, ATT, and ATC
* Matching with subclassification or optimal methods
* Robust sandwich variance estimation
* Balance diagnostics and plotting (e.g., Love plots, QQ plots)
* Federated summary statistics and ECDF-based summaries

---

## Installation

```{r eval = FALSE}
# Install the development version from GitHub
# install.packages("remotes")
remotes::install_github("roygusinow/dsMatchingClient")
```
